File for Figure 4 plots of the Brain Charts paper
Figure 4: Regional Surface Peaks + Cross-Species Alignment (rearrange the plot, monkey, human, differences) (summarize the human peaks as well into cytoarchitecture)
Regional surface peaks for volume, area, and thickness (ADD LINES BETWEEN THE REGIONS ON THE SURFACE)
Bezgin network level peaks by phenotype
Surface peaks post-warping to Desikan-Killiany parcellation (human space)
Associated human regional peaks on the Deskian-Killian parcellation
Difference peaks between human and macaque summarised into the Mesulam cryo-architecture
Difference peaks mapped onto the Deskian-Killiany surface
Plot the human peaks on the lollipop plot of the macaque peak data (the one with the ranges) (order the lollipop plot by the bezgin network) (needs to be in human space) (also generate in macaque space for supplementary or paper)

Most of this stuff is already implemented in Python, but for the sake of consistency and getting it to look 'nice', I'm going to implement in R

First we start with mapping the peaks to the surfaces:

```{r}
## Load the macaque peak data
## Peak data is found in *.COMBAT/peak_CI.rds
getMacaquePeaks <- function() {
  markovOrder <- fromJSON("../../Data/ParcellationMappings/markov_order.json")
  PEAK.LIST <- list()
  for (measure in c("MARKOV.VOLUME.COMBAT", "MARKOV.AREA.COMBAT", "MARKOV.THICKNESS.COMBAT")) {
    PEAK.LIST[[measure]] <- list()
    for (NUM in 1:length(markovOrder)) {
      print(file.path("../../RDS", measure, names(markovOrder)[NUM], "peak_CI.rds"))
      PEAK.LIST[[measure]][[names(markovOrder)[NUM]]] <- readRDS(file.path("../../RDS", measure, names(markovOrder)[NUM], "peak_CI.rds"))
    }
  }
  return(PEAK.LIST)
}

PEAK.LIST <- getMacaquePeaks()
```

FINAL PEAK GENERATION

```{r}
## Now we can visualize peaks on the surface
Visualize.Surface <- function(lh_data, rh_data, species, parcellation, save_location, color_map, color_range_min, color_range_max) {
  setwd("/Users/Sam.Alldritt/Documents/CMI/PRIME-DE/MacaqueCharts-Code-Release")
  write.table(lh_data, "Plotting/temp_lh_data.csv", col.names = FALSE, row.names = FALSE)
  write.table(rh_data, "Plotting/temp_rh_data.csv", col.names = FALSE, row.names = FALSE)
  system(paste("python3", "Plotting/Surface.Plotting.py", parcellation, species, save_location, color_map, color_range_min, color_range_max, "Plotting/temp_lh_data.csv", "Plotting/temp_rh_data.csv", sep = " "))
}

createVisualization <- function(PEAK.LIST, measure, color_map, color_range_min, color_range_max, species, parcellation) {
  setwd("/Users/Sam.Alldritt/Documents/CMI/PRIME-DE/MacaqueCharts-Code-Release/Plotting/Final")
  MVal <- c(0, sapply(PEAK.LIST, function(X) {X$Male_Peak-0.452}))
  FVal <- c(0, sapply(PEAK.LIST, function(X) {X$Female_Peak-0.452}))
  AverageVals <- (MVal + FVal) / 2
  savePath <- file.path("/Users/Sam.Alldritt/Documents/CMI/PRIME-DE/MacaqueCharts-Code-Release/Plotting/Final/Figure3Images/MacaquePeaks", paste(measure, "peak", sep="_"))
  MSP <- paste(savePath, "M.png", sep="_")
  FSP <- paste(savePath, "F.png", sep="_")
  ASP <- paste(savePath, "Ave.svg", sep="_")
  Visualize.Surface(MVal, MVal, species, parcellation, MSP, color_map, color_range_min, color_range_max)
  Visualize.Surface(FVal, FVal, species, parcellation, FSP, color_map, color_range_min, color_range_max)
  Visualize.Surface(AverageVals, AverageVals, species, parcellation, ASP, color_map, color_range_min, color_range_max)
}

createVisualization(PEAK.LIST[["MARKOV.VOLUME.COMBAT"]], "Volume", "RdYlBu_r", 0, 6, "monkey", "markov")
createVisualization(PEAK.LIST[["MARKOV.AREA.COMBAT"]], "Area", "RdYlBu_r", 0, 6, "monkey", "markov")
createVisualization(PEAK.LIST[["MARKOV.THICKNESS.COMBAT"]], "Thickness", "RdYlBu_r", 0, 6, "monkey", "markov")
```

## Get average CI range for volume, thickness, area

```{r}
getAverageCIRange <- function(PEAK.LIST, measure) {
  PEAK.LIST <- lapply(PEAK.LIST, function(X) {
    X <- X - 0.452
    X$Male_Range <- abs(X$Male_Peak_Lower - X$Male_Peak_Upper)
    X$Female_Range <- abs(X$Female_Peak_Lower - X$Female_Peak_Upper)
    return(X)
  })
  male_ranges <- unlist(lapply(PEAK.LIST, function(X) X$Male_Range))
  average_male_range <- mean(male_ranges, na.rm = TRUE)
  sd_male_range <- sd(male_ranges, na.rm = TRUE)
  print(average_male_range)
  print(sd_male_range)
}
getAverageCIRange(PEAK.LIST[["MARKOV.THICKNESS.COMBAT"]], "Volume")
```

```{r}
## Now make a lollipop plot of the peaks and its confidence intervals
lollipopMacaque <- function(PEAK.LIST, measure, sortedDescending=TRUE) {
  library(ggplot2)
  PEAK.LIST <- lapply(PEAK.LIST, function(X) {
    X <- X - 0.452
    X$Male_Range <- abs(X$Male_Peak_Lower - X$Male_Peak_Upper)
    X$Female_Range <- abs(X$Female_Peak_Lower - X$Female_Peak_Upper)
    return(X)
  })
  male_peaks <- sapply(PEAK.LIST, function(x) x$Male_Peak)
  average_male_peak <- mean(male_peaks)

  PEAK.LIST <- bind_rows(PEAK.LIST, .id = "region")
  if (sortedDescending == TRUE) {
    PEAK.LIST.M <- PEAK.LIST[order(PEAK.LIST$Male_Peak), ]
    PEAK.LIST.F <- PEAK.LIST[order(PEAK.LIST$Female_Peak), ]
    PEAK.LIST.M$region <- factor(row.names(PEAK.LIST.M), levels = row.names(PEAK.LIST.M)[order(PEAK.LIST.M$Male_Peak)])
    PEAK.LIST.F$region <- factor(row.names(PEAK.LIST.F), levels = row.names(PEAK.LIST.F)[order(PEAK.LIST.F$Female_Peak)])
  }

  PEAK.LIST.M <- PEAK.LIST.M %>%
    mutate(Male_Peak_Upper = ifelse((Male_Peak_Upper - Male_Peak) > 10, 9, Male_Peak_Upper))

  # Now plot
  male.scatter <- ggplot() +
    geom_point(data = PEAK.LIST.M, aes(x = Male_Peak, y = region, color = Male_Range), size = 8, alpha = 0.5) +
    geom_vline(xintercept = average_male_peak, color="black", linetype = "dashed", size=1.5) +
    geom_errorbarh(data = PEAK.LIST.M, aes(xmin = Male_Peak_Lower, xmax = Male_Peak_Upper, y = region), height = 0.1) +
    ylab("Regions") +
    xlab("Age Peak (yrs)") +
    ggtitle(measure) +
    theme_classic() +
    scale_color_gradient(low = "gray", high = "red", limits = c(0, 10)) +
    labs(color = "CI Range (yrs)") +
    theme(
      panel.grid.major.y = element_line(color = "gray", linetype = "dashed", size = 0.3),
      axis.text.y = element_text(size = 18),
      axis.title.x = element_text(size=22),
      axis.text.x = element_text(size=18),
      title = element_text(size=24),
      legend.text = element_text(size = 22),
    ) +
    ggeasy::easy_center_title()

  if (measure == "MARKOV.VOLUME.COMBAT") {
    male.scatter <- male.scatter + xlim(c(0, 11))
  } else if (measure == "MARKOV.AREA.COMBAT") {
    male.scatter <- male.scatter + xlim(c(0, 15))
  } else if (measure == "MARKOV.THICKNESS.COMBAT") {
    male.scatter <- male.scatter + xlim(c(0, 7.5))
  }

  female.scatter <- ggplot() +
    geom_point(data = PEAK.LIST.F, aes(x = Female_Peak, y = region, color = Female_Range), size = 5, alpha = 0.5) +
    geom_errorbarh(data = PEAK.LIST.F, aes(xmin = Female_Peak_Lower, xmax = Female_Peak_Upper, y = region), height = 0.1) +
    ylab("Regions") +
    xlab("Age Peak (yrs)") +
    theme_classic() +
    scale_color_gradient(low = "gray", high = "red") +
    theme(
      panel.grid.major.y = element_line(color = "gray", linetype = "dashed", size = 0.3),
      axis.text.y = element_text(size = 10)
    )

  ggsave(file.path("Figure3Images/Peak.CI/MacaqueOnly", paste0("M_", measure, ".png")), plot=male.scatter, width=8, height=12)
  ggsave(file.path("Figure3Images/Peak.CI/MacaqueOnly", paste0("F_", measure, ".png")), plot=female.scatter, width=8, height=12)
  return(male.scatter)
}
vol <- lollipopMacaque(PEAK.LIST[["MARKOV.VOLUME.COMBAT"]], "Volume")
area <- lollipopMacaque(PEAK.LIST[["MARKOV.AREA.COMBAT"]], "Area")
thickness <- lollipopMacaque(PEAK.LIST[["MARKOV.THICKNESS.COMBAT"]], "Thickness")
final <- vol + area + thickness +
  plot_layout(
    axis_titles = "collect",
    guides="collect"
  )
ggsave(file.path("Figure3Images/Peak.CI/MacaqueOnly", paste0("M.png")), plot=final, width=32, height=20)
ggsave(file.path("Figure3Images/Peak.CI/MacaqueOnly", paste0("M.pdf")), plot=final, width=32, height=20)
```

```{r}
## Load in and visualize the human peaks
# ALREADY VISUALIZED
```

```{r}
## Summarize the macaque peaks on the bezgin network level
## First create func.gifti files
createMacaquePeakGifti <- function(MVal, FVal, measure) {
  write.table(MVal, "Figure3Scripts/temp_MVal.csv", col.names=FALSE, row.names=FALSE)
  write.table(FVal, "Figure3Scripts/temp_FVal.csv", col.names=FALSE, row.names=FALSE)
  system(paste("python3", "Figure3Scripts/mapToSurface.py", "--lh-csv", "Figure3Scripts/temp_MVal.csv", "--rh-csv", "Figure3Scripts/temp_MVal.csv", "--parcellation", "markov", "--save-prefix", paste0("Figure3Data/MacaquePeaks/func.gifti.markov/", "M.", measure)))
  system(paste("python3", "Figure3Scripts/mapToSurface.py", "--lh-csv", "Figure3Scripts/temp_FVal.csv", "--rh-csv", "Figure3Scripts/temp_FVal.csv", "--parcellation", "markov", "--save-prefix", paste0("Figure3Data/MacaquePeaks/func.gifti.markov/", "F.", measure)))
}
M <- c(0, unlist(sapply(PEAK.LIST[["MARKOV.THICKNESS.COMBAT"]], function(X) {X$Male_Peak})))
F <- c(0, unlist(sapply(PEAK.LIST[["MARKOV.THICKNESS.COMBAT"]], function(X) {X$Female_Peak})))
createMacaquePeakGifti(M, F, "Thickness")
```

```{r}
## Now summarize the func GIFTI files (macaque space) into the bezgin network and plot results
mapMarkov2Bezgin <- function(lh_path, rh_path, save_prefix) {
  system(paste("python3", "Figure3Scripts/mapParcellation2Cryoarchitecture.py", "--surface", "markov", "--lh-path", lh_path, "--rh-path", rh_path, "--save-prefix", save_prefix, "--parcellation", "bezgin"))
}

mapMarkov2Bezgin(
  "Figure3Data/MacaquePeaks/func.gifti.markov/M.Volume.lh.func.gii",
  "Figure3Data/MacaquePeaks/func.gifti.markov/M.Volume.rh.func.gii",
  "Figure3Data/MacaquePeaks/func.gifti.bezgin/M.Volume"
  )
mapMarkov2Bezgin(
  "Figure3Data/MacaquePeaks/func.gifti.markov/F.Volume.lh.func.gii",
  "Figure3Data/MacaquePeaks/func.gifti.markov/F.Volume.rh.func.gii",
  "Figure3Data/MacaquePeaks/func.gifti.bezgin/F.Volume"
)
mapMarkov2Bezgin(
  "Figure3Data/MacaquePeaks/func.gifti.markov/M.Area.lh.func.gii",
  "Figure3Data/MacaquePeaks/func.gifti.markov/M.Area.rh.func.gii",
  "Figure3Data/MacaquePeaks/func.gifti.bezgin/M.Area"
)
mapMarkov2Bezgin(
  "Figure3Data/MacaquePeaks/func.gifti.markov/F.Area.lh.func.gii",
  "Figure3Data/MacaquePeaks/func.gifti.markov/F.Area.rh.func.gii",
  "Figure3Data/MacaquePeaks/func.gifti.bezgin/F.Area"
)
mapMarkov2Bezgin(
  "Figure3Data/MacaquePeaks/func.gifti.markov/M.Thickness.lh.func.gii",
  "Figure3Data/MacaquePeaks/func.gifti.markov/M.Thickness.rh.func.gii",
  "Figure3Data/MacaquePeaks/func.gifti.bezgin/M.Thickness"
)
mapMarkov2Bezgin(
  "Figure3Data/MacaquePeaks/func.gifti.markov/F.Thickness.lh.func.gii",
  "Figure3Data/MacaquePeaks/func.gifti.markov/F.Thickness.rh.func.gii",
  "Figure3Data/MacaquePeaks/func.gifti.bezgin/F.Thickness"
)
```

```{r}
library(patchwork)
## Now load in the bezgin data and make plots for volume, thickness, and area
bezginBarPlot <- function(data_path, sem_path, type) {
  library(ggplot2)
  regions <- c("Default1", "Somatomotor", "Auditory", "Limbic", "DorsalAtt", "Visual", "Insular-Opecular")
  data <- read.csv(data_path, col.names="mean")
  sem <- read.csv(sem_path)
  data$sem <- sem[,1]
  data$region <- regions

  plot <- ggplot(data, aes(x = region, y = mean, fill=region)) +
    geom_col() +
    geom_errorbar(aes(ymin = mean - sem, ymax = mean + sem), width = 0.2) +
    scale_fill_manual(values=c(
      "Default1" = "#CB816F",
      "Somatomotor" = "#8BB0D7",
      "Auditory" = "#FCFFAB",
      "Limbic" = "#B7E058",
      "DorsalAtt" = "#EAB557",
      "Visual" = "#A28DFF",
      "Insular-Opecular" = "#99D3C7")) +
    ylab("Peak Age") +
    xlab("") +
    ggtitle(type) +
    ylim(0, 3) +
    theme_classic() +
    theme(
      axis.text.y = element_text(size = 15),
      legend.text = element_text(size = 15),
      legend.title = element_blank(),  # Remove legend title
      axis.text.x = element_blank(),  # Remove x-axis labels
      axis.ticks.x = element_blank(),  # Remove x-axis ticks
      plot.margin = unit(c(0, 0, 0, 0), "cm")
    ) +
    ggeasy::easy_center_title()

  ggsave(file.path("Figure3Images/BezginPeak", paste0("Bezgin.M.L.", type, ".png")), plot=plot, width=6, height=4)
  return(plot)
}
BezginVol <- bezginBarPlot(
  "Figure3Data/MacaquePeaks/peak.csv.bezgin/M.Volume.L.csv",
  "Figure3Data/MacaquePeaks/peak.csv.bezgin/M.Volume.SEM.L.csv",
  "Volume"
  )
BezginArea <- bezginBarPlot(
  "Figure3Data/MacaquePeaks/peak.csv.bezgin/M.Area.L.csv",
  "Figure3Data/MacaquePeaks/peak.csv.bezgin/M.Area.SEM.L.csv",
  "Area"
)
BezginThickness <- bezginBarPlot(
  "Figure3Data/MacaquePeaks/peak.csv.bezgin/M.Thickness.L.csv",
  "Figure3Data/MacaquePeaks/peak.csv.bezgin/M.Thickness.SEM.L.csv",
  "Thickness"
)
bezginPlot <- BezginVol + BezginArea + BezginThickness +
  plot_layout(
    axis_titles = "collect",
    guides = "collect",
  )
#ggsave("Figure3Images/BezginPeak/Bezgin.M.L.pdf", plot=bezginPlot, width=12, height=4)
bezginPlot
```

```{r}
## Call bash file to map from macaque space to human space
system(paste("bash", "Figure3Scripts/map2human.sh"))
```

```{r}
## Summarize the markov parcellation in human space into aparc (with csv peaks and metric files)
system(paste("bash", "Figure3Scripts/loopRemapMarkov2Human.sh"))
```

```{r}
## Generate mesulam
mapAparc2Mesulam <- function(lh_path, rh_path, save_prefix) {
  system(paste("python3", "Figure3Scripts/mapParcellation2Cryoarchitecture.py", "--lh-path", lh_path, "--rh-path", rh_path, "--save-prefix", save_prefix, "--parcellation", "mesulam"))
}

mapAparc2Mesulam(
  "Figure3Data/MacaquePeaksInHuman/aparc/gifti/M.Volume.lh.func.gii",
  "Figure3Data/MacaquePeaksInHuman/aparc/gifti/M.Volume.rh.func.gii",
  "Figure3Data/MacaquePeaksInHuman/aparc/aparc2Mesulam/M.Volume"
  )
mapAparc2Mesulam(
  "Figure3Data/MacaquePeaksInHuman/aparc/gifti/M.Area.lh.func.gii",
  "Figure3Data/MacaquePeaksInHuman/aparc/gifti/M.Area.rh.func.gii",
  "Figure3Data/MacaquePeaksInHuman/aparc/aparc2Mesulam/M.Area"
  )
mapAparc2Mesulam(
  "Figure3Data/MacaquePeaksInHuman/aparc/gifti/M.Thickness.lh.func.gii",
  "Figure3Data/MacaquePeaksInHuman/aparc/gifti/M.Thickness.rh.func.gii",
  "Figure3Data/MacaquePeaksInHuman/aparc/aparc2Mesulam/M.Thickness"
  )
mapAparc2Mesulam(
  "Figure3Data/MacaquePeaksInHuman/aparc/gifti/F.Volume.lh.func.gii",
  "Figure3Data/MacaquePeaksInHuman/aparc/gifti/F.Volume.rh.func.gii",
  "Figure3Data/MacaquePeaksInHuman/aparc/aparc2Mesulam/F.Volume"
  )
mapAparc2Mesulam(
  "Figure3Data/MacaquePeaksInHuman/aparc/gifti/F.Area.lh.func.gii",
  "Figure3Data/MacaquePeaksInHuman/aparc/gifti/F.Area.rh.func.gii",
  "Figure3Data/MacaquePeaksInHuman/aparc/aparc2Mesulam/F.Area"
  )
mapAparc2Mesulam(
  "Figure3Data/MacaquePeaksInHuman/aparc/gifti/F.Thickness.lh.func.gii",
  "Figure3Data/MacaquePeaksInHuman/aparc/gifti/F.Thickness.rh.func.gii",
  "Figure3Data/MacaquePeaksInHuman/aparc/aparc2Mesulam/F.Thickness"
  )
```

```{r}
## Load in and plot the lollipop plot of the human vs macaque peaks (also have to normalize) (?)
loadHumanMacaqueAparcPeaks <- function() {
  ## Load in the peaks for both species (TotalGrayVol, SurfaceArea, CorticalThickness)
  aparcLabels <- fromJSON(file="../../Data/ParcellationMappings/aparc_order.json")
  MesulamNames <- c("Paralimbic", "High-order Association", "Modality-specific Association", "Idiotypic (primary)")
  MesulamMapping <- read.csv("Figure3Data/MacaquePeaksInHuman/aparc/aparc2Mesulam/M.Volume.mapping.L.csv", header=FALSE, col.names="MesulamLabels")
  MesulamMapping <- MesulamMapping %>%
    mutate(MesulamNames = MesulamNames[MesulamLabels])
  PEAKS <- list()
  PEAKS[["Volume"]] <- data.frame(
    Macaque = read.csv("Figure3Data/MacaquePeaksInHuman/aparc/csv/M.Volume.lh.csv", header=FALSE, col.names="Macaque"),
    Human = read.csv("Figure3Data/HumanPeaks/volume_peak.csv", header=FALSE, col.names="Human"),
    AparcNames = c("unknown", names(aparcLabels)),
    MesulamLabels = MesulamMapping$MesulamLabels,
    MesulamNames = MesulamMapping$MesulamNames
  )
  PEAKS[["Area"]] <- data.frame(
    Macaque = read.csv("Figure3Data/MacaquePeaksInHuman/aparc/csv/M.Area.lh.csv", header=FALSE, col.names="Macaque"),
    Human = read.csv("Figure3Data/HumanPeaks/area_peaks.csv", header=FALSE, col.names="Human"),
    AparcNames = c("unknown", names(aparcLabels)),
    MesulamLabels = MesulamMapping$MesulamLabels,
    MesulamNames = MesulamMapping$MesulamNames
  )
  PEAKS[["Thickness"]] <- data.frame(
    Macaque = read.csv("Figure3Data/MacaquePeaksInHuman/aparc/csv/M.Thickness.lh.csv", header=FALSE, col.names="Macaque"),
    Human = read.csv("Figure3Data/HumanPeaks/thickness_peaks.csv", header=FALSE, col.names="Human"),
    AparcNames = c("unknown", names(aparcLabels)),
    MesulamLabels = MesulamMapping$MesulamLabels,
    MesulamNames = MesulamMapping$MesulamNames
  )
  saveRDS(PEAKS, "Figure3Data/HumanMacaqueAparcPeaks.rds")
  return(PEAKS)
}
aparcPeaks <- loadHumanMacaqueAparcPeaks()
```

```{r}
## Plot macaque surfaces in human space
Visualize.Surface <- function(lh_data, rh_data, species, parcellation, save_location, color_map, color_range_min, color_range_max) {
  setwd("/Users/Sam.Alldritt/Documents/CMI/PRIME-DE/MacaqueCharts-Code-Release")
  write.table(lh_data, "Plotting/temp_lh_data.csv", col.names = FALSE, row.names = FALSE)
  write.table(rh_data, "Plotting/temp_rh_data.csv", col.names = FALSE, row.names = FALSE)
  system(paste("python3", "Plotting/Surface.Plotting.py", parcellation, species, save_location, color_map, color_range_min, color_range_max, "Plotting/temp_lh_data.csv", "Plotting/temp_rh_data.csv", sep = " "))
}

createVisualization <- function(MVal, measure, color_map, color_range_min, color_range_max, species, parcellation) {
  setwd("/Users/Sam.Alldritt/Documents/CMI/PRIME-DE/MacaqueCharts-Code-Release/Plotting/Final")
  savePath <- file.path("/Users/Sam.Alldritt/Documents/CMI/PRIME-DE/MacaqueCharts-Code-Release/Plotting/Final/Figure3Images/HumanPeaks", paste(measure, "peak", sep="_"))
  MSP <- paste(savePath, "M.png", sep="_")
  Visualize.Surface(MVal, MVal, species, parcellation, MSP, color_map, color_range_min, color_range_max)
}

MVal <- aparcPeaks[['Volume']]$Human
createVisualization(MVal, "Volume", "RdYlBu_r", 0, 16, "human", "aparc")
MVal <- aparcPeaks[['Area']]$Human
createVisualization(MVal, "Area", "RdYlBu_r", 0, 16, "human", "aparc")
MVal <- aparcPeaks[['Thickness']]$Human
createVisualization(MVal, "Thickness", "RdYlBu_r", 0, 6, "human", "aparc")
```

```{r}
## Make a lollipop plot of human and macaque peaks (in human space)
humanMacaqueLollipop <- function(normalizingHumanAge, normalizingMacaqueAge, aparcPeaks, type) {
  library(ggplot2)
  library(ggnewscale)
  aparcPeaks$MacaqueNormalized <- aparcPeaks$Macaque / normalizingMacaqueAge
  aparcPeaks$HumanNormalized <- aparcPeaks$Human / normalizingHumanAge
  aparcPeaks$Range <- aparcPeaks$MacaqueNormalized - aparcPeaks$HumanNormalized
  aparcPeaks$AparcNames <- factor(aparcPeaks$AparcNames, levels = aparcPeaks$AparcNames[order(aparcPeaks$MesulamLabels)])
  scatter <- ggplot() +
    geom_point(data = aparcPeaks, aes(x = MacaqueNormalized, y = reorder(AparcNames, MacaqueNormalized), color="Macaque"), size = 5, alpha = 0.8) +
    geom_point(data = aparcPeaks, aes(x = HumanNormalized, y = reorder(AparcNames, MacaqueNormalized), color="Human"), size = 5, alpha = 0.8) +
    scale_color_manual(
      name = "",
      values = c(Macaque = "#E3170A", Human = "#247BA0")
    ) +
    new_scale_color() +
    geom_segment(
      data = aparcPeaks,
      aes(x = MacaqueNormalized, xend = HumanNormalized + sign(Range) * 0.007, y = reorder(AparcNames, MacaqueNormalized), yend = reorder(AparcNames, MacaqueNormalized), colour=Range),
      size = 0.8,
      alpha=0.6,
      arrow = arrow(type = "open", length = unit(0.07, "inches"))) +
    scale_color_gradientn(
      colors = c("blue","gray", "red"),
      limits = c(-0.2, 0.2),
      oob = scales::squish,
      name="Prop. Age Difference"
    ) +
    ylab("") +
    xlab("Proportional Lifespan Peak") +
    theme_classic() +
    theme(
      panel.grid.major.y = element_line(color = "gray", linetype = "dashed", size = 0.3),
      axis.text.y = element_text(size = 10),
      strip.placement = "outside",
      strip.background = element_blank(),
      panel.spacing = unit(0, "lines"),
      strip.text = element_text(margin = margin(0, 0, 10, 0), size=12)
    ) +
    facet_wrap(~MesulamNames, strip.position="left", scales="free_y", ncol=1)
  ggsave(file.path("Figure3Images/MacaquePeaksInHumanSpace", paste0("aparc.human.macaque.", type, ".png")), plot=scatter, width=6, height=10, dpi=300)
  return (scatter)
}
scatter <- humanMacaqueLollipop(80, 25, aparcPeaks[["Area"]], "Area")
scatter
```

```{r}
## Generate the difference maps (after normalizing for some global metric peak)
Visualize.Surface <- function(lh_data, rh_data, species, parcellation, save_location, color_map, color_range_min, color_range_max) {
  setwd("/Users/Sam.Alldritt/Documents/CMI/PRIME-DE/MacaqueCharts-Code-Release")
  write.table(lh_data, "Plotting/temp_lh_data.csv", col.names = FALSE, row.names = FALSE)
  write.table(rh_data, "Plotting/temp_rh_data.csv", col.names = FALSE, row.names = FALSE)
  system(paste("python3", "Plotting/Surface.Plotting.py", parcellation, species, save_location, color_map, color_range_min, color_range_max, "Plotting/temp_lh_data.csv", "Plotting/temp_rh_data.csv", sep = " "))
}

createVisualization <- function(MVal, measure, color_map, color_range_min, color_range_max, species, parcellation) {
  setwd("/Users/Sam.Alldritt/Documents/CMI/PRIME-DE/MacaqueCharts-Code-Release/Plotting/Final")
  savePath <- file.path("/Users/Sam.Alldritt/Documents/CMI/PRIME-DE/MacaqueCharts-Code-Release/Plotting/Final/Figure3Images/DifferenceMaps/aparc", paste(measure, "peak", sep="_"))
  MSP <- paste(savePath, "M.png", sep="_")
  Visualize.Surface(MVal, MVal, species, parcellation, MSP, color_map, color_range_min, color_range_max)
}

createMacaquePeakGifti <- function(Val, measure) {
  write.table(Val, "Figure3Scripts/temp_Val.csv", col.names=FALSE, row.names=FALSE)
  system(paste("python3", "Figure3Scripts/mapToSurface.py", "--lh-csv", "Figure3Scripts/temp_Val.csv", "--rh-csv", "Figure3Scripts/temp_Val.csv", "--parcellation", "aparc", "--save-prefix", paste0("Figure3Data/MacaquePeaksInHuman/aparc/DifferenceMaps/", "M.", measure)))
}

generateDifferenceMaps <- function(aparcPeaks, type, normalizingHumanAge, normalizingMacaqueAge) {
  aparcPeaks$MacaqueNormalized <- aparcPeaks$Macaque / normalizingMacaqueAge
  aparcPeaks$HumanNormalized <- aparcPeaks$Human / normalizingHumanAge
  aparcPeaks$Difference <- aparcPeaks$HumanNormalized - aparcPeaks$MacaqueNormalized
  aparcPeaks$Difference[1] <- 0
  createMacaquePeakGifti(aparcPeaks$Difference, type)
  createVisualization(aparcPeaks$Difference, type, "coolwarm", -0.2, 0.2, "human", "aparc")
  return(aparcPeaks)
}
aparcPeaks[["Volume"]] <- generateDifferenceMaps(aparcPeaks[['Volume']], "Volume", 80, 25)
aparcPeaks[["Area"]] <- generateDifferenceMaps(aparcPeaks[['Area']], "Area", 80, 25)
aparcPeaks[["Thickness"]] <- generateDifferenceMaps(aparcPeaks[['Thickness']], "Thickness", 80, 25)
```

```{r}
## Load in and plot the mesulam data
library(ggplot2)
library(patchwork)
mesulamBarPlot <- function(aparcPeaks, type) {
  summary <- aparcPeaks %>%
    group_by(MesulamNames) %>%
    slice(-1) %>%
    summarise(
      mean_diff = mean(Difference),
      sem_diff = (sd(Difference) / n())
    )

  plot <- ggplot(summary, aes(x = MesulamNames, y = mean_diff, fill=MesulamNames)) +
    geom_col() +
    geom_errorbar(aes(ymin = mean_diff - sem_diff, ymax = mean_diff + sem_diff), width = 0.2) +
    scale_fill_manual(values=c(
      "Paralimbic" = '#83B540',
      "High-order Association" = '#F5A190',
      "Modality-specific Association" = '#F2F45D',
      "Idiotypic (primary)" = '#7C9ECF')) +
    ylab("Lifespan Peak Difference") +
    xlab("") +
    #ggtitle(type) +
    #ylim(0, 3) +
    theme_classic() +
    theme(
      legend.text = element_text(size=15),
      axis.text.y = element_text(size=15),
      legend.title = element_blank(),  # Remove legend title
      axis.text.x = element_blank(),  # Remove x-axis labels
      axis.ticks.x = element_blank(),  # Remove x-axis ticks
      plot.margin = unit(c(0, 0, 0, 0), "cm")
    ) +
    ggeasy::easy_center_title()
  ggsave(file.path("Figure3Images/MesulamDiff", paste0("Mesulam.M.L.", type, ".png")), plot=plot, width=6, height=4)
  return(plot)
}

MesulamVol <- mesulamBarPlot(aparcPeaks[["Volume"]], "Volume")
MesulamArea <- mesulamBarPlot(aparcPeaks[["Area"]], "Area")
MesulamThickness <- mesulamBarPlot(aparcPeaks[["Thickness"]], "Thickness")
mesulamPlot <- MesulamVol + MesulamArea + MesulamThickness +
  plot_layout(
    axis_titles = "collect",
    guides = "collect",
  )
ggsave("Figure3Images/MesulamDiff/Mesulam.M.L.pdf", plot=mesulamPlot, width=12, height=4)
mesulamPlot
```

```{r}
## Add mesulam vol, area, thickness together with bezgin
Vol <- BezginVol / MesulamVol
ggsave("Figure3Images/MesulamDiff/MesulamBezgin.M.L.Vol.png", plot=Vol, width=6, height=4)
Area <- BezginArea / MesulamArea
ggsave("Figure3Images/MesulamDiff/MesulamBezgin.M.L.Area.png", plot=Area, width=6, height=4)
Thickness <- BezginThickness / MesulamThickness & theme(legend.text = element_text(size=12))
ggsave("Figure3Images/MesulamDiff/MesulamBezgin.M.L.Thickness.png", plot=Thickness, width=6, height=4)
```

Map back to volume space
Feed volumes into neuroquery

```{r}
system(paste("bash", "Figure3Scripts/metric2volume_RC.sh"))
```

```{r}
lh_aparc <- "../../Atlas/aparc/fs_LR.aparc.L.32k.func.gii"
rh_aparc <- "../../Atlas/aparc/fs_LR.aparc.R.32k.func.gii"
base_metric_path <- "Figure3Data/MacaquePeaksInHuman/aparc/DifferenceMaps"
n_terms <- 200
n_studies <- 10

system(paste("python3", "Figure3Scripts/image_search.py",
             "--image-path", file.path(base_metric_path, "volumes", "M.Volume.nii.gz"),
             "--n-studies", n_studies,
             "--n-terms", n_terms,
             "--pos-neg",
             "--bins", 4,
             "--output", file.path(base_metric_path, "neuroquery", "M.Volume")))
system(paste("python3", "Figure3Scripts/image_search.py",
             "--image-path", file.path(base_metric_path, "volumes", "M.Area.nii.gz"),
             "--n-studies", n_studies,
             "--n-terms", n_terms,
             "--pos-neg",
             "--bins", 4,
             "--output", file.path(base_metric_path, "neuroquery", "M.Area")))
system(paste("python3", "Figure3Scripts/image_search.py",
             "--image-path", file.path(base_metric_path, "volumes", "M.Thickness.nii.gz"),
             "--n-studies", n_studies,
             "--n-terms", n_terms,
             "--pos-neg",
             "--bins", 4,
             "--output", file.path(base_metric_path, "neuroquery", "M.Thickness")))
```

Map to labels

```{r}
loadKeys <- function() {
  topics_to_keep = c(1, 4,  6, 14,
                  18, 23, 25,
                  20, 21, 27, 29,
                  30, 31, 33, 35,
                  36, 38, 41,
                  44, 45, 48, 49
                  )
  labels = c('affective processing', ' verbal semantics', 'cued attention', 'working memory',
          'autobiographical memory', 'inhibition', 'motor',
          'visual perception', 'numerical cognition', 'reward-based decision making', 'visual attention',
          'multisensory processing', 'visuospatial','eye movements', 'action',
          'auditory processing', 'pain', 'declarative memory',
          'visual semantics', 'emotion', 'cognitive control', 'social cognition'
          )
  keys <- read.csv("Figure3Scripts/v3-topics-50-keys.txt", sep = "\t", header = FALSE, row.names = 1)
  keys <- keys[topics_to_keep, , drop = FALSE]
  keys$labels <- labels
  colnames(keys) <- c("unknown", "words", "labels")
  return(keys)
}

mapLabels <- function(path, type, lowerBin, upperBin) {
  result <- list()
  lower_bins <- sapply(1:lowerBin, function(X) { paste0("negative/bin_", X) })
  upper_bins <- sapply(upperBin:4, function(X) { paste0("positive/bin_", X) })
  terms <- list()
  for (bin in c(lower_bins, upper_bins)) {
    term_lines <- readLines(file.path(path, "neuroquery", type, bin, "terms.json"))
    terms[[bin]] <- as.data.frame(do.call(rbind, lapply(term_lines, function(line) fromJSON(line, flatten = TRUE))))
    terms[[bin]]$bin <- bin
    if (bin %in% lower_bins) {
      terms[[bin]]$scale <- "negative"
    } else {
      terms[[bin]]$scale <- "positive"
    }
  }
  find_label <- function(term) {
    matched_label <- keys$labels[str_detect(keys$words, term)]
    if (length(matched_label) > 0) {
      return(matched_label[1])
    } else {
      return(NA)
    }
  }
  terms <- lapply(terms, function(X) {
    X$label <- sapply(X$term, find_label)
    return(X)
  })
  terms <- lapply(terms, function(X) {
    X <- X %>%
      filter(similarity > 0.5, !is.na(label)) %>%
      mutate(similarity = as.numeric(similarity)) %>%
      mutate(score = ifelse(scale == "negative", -(similarity), similarity))
    return(X)
  })
  terms <- bind_rows(terms)
  saveRDS(terms, file.path(path, "neuroquery", type, "mappedTerms.rds"))
  result[[1]] <- as.data.frame(terms)
  result <- Reduce(bind_rows, result)

  ## Summarise the labels
  result <- as.data.frame(result) %>%
    group_by(scale) %>%
    mutate(total_score = abs(score)) %>%
    arrange(total_score) %>%
    mutate(rank = row_number()) %>%
    filter(rank <= 10) %>%
    ungroup()

  result <- result %>%
    group_by(label) %>%
    slice(which.max(total_score))

  return(result)
}

generateWordCloud <- function(terms, savePath) {

  data <- terms %>%
    group_by(label, scale) %>%
    summarize(freq = rank) %>%
    mutate(color = ifelse(scale == "negative", "blue", "red"))

  print(file.path(getwd(), savePath, "summaryTerms.rds"))
  saveRDS(data, file.path(savePath, "summaryTerms.rds"))
  wordcloud_data <- data.frame(word = as.character(data$label), freq = data$freq, color=data$color)
  plot <- wordcloud2(wordcloud_data, size = .5, color = wordcloud_data$color, backgroundColor = "white", maxRotation = 0, minRotation = 0)
  saveWidget(plot, file = file.path(savePath, "wordcloud2.html"))
  webshot::webshot(file.path(savePath, "wordcloud2.html"), file.path(savePath, "wordcloud2.png"), vwidth = 1000, vheight = 1000, delay=10)
  return(plot)
}

keys <- loadKeys()
allTerms <- mapLabels("Figure3Data/MacaquePeaksInHuman/aparc/DifferenceMaps", "M.Volume.Ranked", 1, 4)
generateWordCloud(allTerms, "Figure3Data/MacaquePeaksInHuman/aparc/DifferenceMaps/neuroquery/M.Volume.Ranked")
```

Rank the difference maps and map them on to x and y coordinates

```{r}
generateRankedMapping <- function(aparcPeaks, type) {
  aparcPeaks$MacaqueRanked <- rank(aparcPeaks$Macaque)
  aparcPeaks$HumanRanked <- rank(aparcPeaks$Human)
  aparcPeaks$RankDiff <- aparcPeaks$HumanRanked - aparcPeaks$MacaqueRanked
  aparcPeaks$color <- ifelse(aparcPeaks$RankDiff > 0, "#247BA0", "#E3170A")

  aparcPeaks <- aparcPeaks %>%
    arrange(HumanRanked)

  labelData <- aparcPeaks %>%
    arrange(MacaqueRanked)

  plot <- ggplot(data=aparcPeaks, aes(x=HumanRanked, y=MacaqueRanked, color = MesulamNames)) +
    geom_point(size=3) +
    scale_x_continuous(
      breaks = seq(1, 36),
      labels = aparcPeaks$AparcNames
      ) +
    scale_y_continuous(
      breaks = seq(1, 36),
      labels = labelData$AparcNames
    ) +
    scale_color_manual(values=c(
      "Paralimbic" = '#83B540',
      "High-order Association" = '#F5A190',
      "Modality-specific Association" = '#F2F45D',
      "Idiotypic (primary)" = '#7C9ECF'
      )) +
    labs(color = "Mesulam Regions") +
    new_scale_color() +
    geom_segment(
      data = aparcPeaks,
      aes(x = HumanRanked, xend = HumanRanked, y = MacaqueRanked, yend = HumanRanked, colour=RankDiff),
      size = 0.8,
      alpha=0.8,
      linetype = "dashed",
      show.legend = FALSE
      ) +
    scale_color_gradientn(
      colors = c("blue","gray", "red"),
      limits = c(-20, 20),
      oob = scales::squish,
      name="Prop. Rank Difference"
    ) +
    xlab("Human") +
    ylab("Macaque") +
    geom_abline(intercept = 0, slope = 1, linetype = "dashed", color = "black") +
    theme_classic() +
    ggtitle(type) +
    ggeasy::easy_center_title() +
    theme(
      axis.text.x = element_text(angle = 45, hjust = 1),
      plot.title = element_text(size = 16, face = "bold"),
      legend.text = element_text(size = 12),
      legend.title = element_text(size = 14),
      legend.key.size = unit(2, "lines")
    )

  return(plot)
}
vol <- generateRankedMapping(aparcPeaks$Volume, "Volume")
area <- generateRankedMapping(aparcPeaks$Area, "Area")
thickness <- generateRankedMapping(aparcPeaks$Thickness, "Thickness")
plot <- vol + area + thickness +
  plot_layout(
    guides = "collect",
    axis_titles = "collect",
  ) & theme(
    legend.position = "bottom"
  )
ggsave(plot=plot, file.path("Figure3Images/DifferenceMaps/RankedSummary.png"), width=20, height=6, dpi=300)
```

```{r}
Visualize.Surface <- function(lh_data, rh_data, species, parcellation, save_location, color_map, color_range_min, color_range_max) {
  setwd("/Users/Sam.Alldritt/Documents/CMI/PRIME-DE/MacaqueCharts-Code-Release")
  write.table(lh_data, "Plotting/temp_lh_data.csv", col.names = FALSE, row.names = FALSE)
  write.table(rh_data, "Plotting/temp_rh_data.csv", col.names = FALSE, row.names = FALSE)
  system(paste("python3", "Plotting/Surface.Plotting.py", parcellation, species, save_location, color_map, color_range_min, color_range_max, "Plotting/temp_lh_data.csv", "Plotting/temp_rh_data.csv", sep = " "))
}
## Function for mapping the ranking onto the surface
mapRankSurface <- function(aparcPeaks, type, color) {
  aparcPeaks$MacaqueRanked <- rank(aparcPeaks$Macaque)
  aparcPeaks$HumanRanked <- rank(aparcPeaks$Human)
  aparcPeaks$RankDiff <- aparcPeaks$HumanRanked - aparcPeaks$MacaqueRanked
  savePathMacaque <- file.path("Plotting/Final/Figure3Images/DifferenceMaps", paste0("M.", type, "MacaqueRanked.png"))
  savePathHuman <- file.path("Plotting/Final/Figure3Images/DifferenceMaps", paste0("M.", type, "HumanRanked.png"))
  savePathDiff <- file.path("Plotting/Final/Figure3Images/DifferenceMaps", paste0("M.", type, "DiffRanked.png"))
  macaqueVals <- aparcPeaks$MacaqueRanked
  humanVals <- aparcPeaks$HumanRanked
  diffVals <- aparcPeaks$RankDiff
  Visualize.Surface(macaqueVals, macaqueVals, "human", "aparc", savePathMacaque, color, 0, 36)
  Visualize.Surface(humanVals, humanVals, "human", "aparc", savePathHuman, color, 0, 36)
  Visualize.Surface(diffVals, diffVals, "human", "aparc", savePathDiff, "coolwarm", -20, 20)
}

mapRankSurface(aparcPeaks[["Volume"]], "Volume", "Reds")
mapRankSurface(aparcPeaks[["Area"]], "Area", "Reds")
mapRankSurface(aparcPeaks[["Thickness"]], "Thickness", "Reds")
```

```{r}
## Generate the difference maps (after normalizing for some global metric peak)
Visualize.Surface <- function(lh_data, rh_data, species, parcellation, save_location, color_map, color_range_min, color_range_max) {
  setwd("/Users/Sam.Alldritt/Documents/CMI/PRIME-DE/MacaqueCharts-Code-Release")
  write.table(lh_data, "Plotting/temp_lh_data.csv", col.names = FALSE, row.names = FALSE)
  write.table(rh_data, "Plotting/temp_rh_data.csv", col.names = FALSE, row.names = FALSE)
  system(paste("python3", "Plotting/Surface.Plotting.py", parcellation, species, save_location, color_map, color_range_min, color_range_max, "Plotting/temp_lh_data.csv", "Plotting/temp_rh_data.csv", sep = " "))
}

createVisualization <- function(MVal, measure, color_map, color_range_min, color_range_max, species, parcellation) {
  setwd("/Users/Sam.Alldritt/Documents/CMI/PRIME-DE/MacaqueCharts-Code-Release/Plotting/Final")
  savePath <- file.path("/Users/Sam.Alldritt/Documents/CMI/PRIME-DE/MacaqueCharts-Code-Release/Plotting/Final/Figure3Images/DifferenceMaps/aparc", paste(measure, "ranked", sep="_"))
  MSP <- paste(savePath, "M.png", sep="_")
  Visualize.Surface(MVal, MVal, species, parcellation, MSP, color_map, color_range_min, color_range_max)
}

createMacaquePeakGifti <- function(Val, measure) {
  setwd("/Users/Sam.Alldritt/Documents/CMI/PRIME-DE/MacaqueCharts-Code-Release/Plotting/Final")
  write.table(Val, "Figure3Scripts/temp_Val.csv", col.names=FALSE, row.names=FALSE)
  system(paste("python3", "Figure3Scripts/mapToSurface.py", "--lh-csv", "Figure3Scripts/temp_Val.csv", "--rh-csv", "Figure3Scripts/temp_Val.csv", "--parcellation", "aparc", "--save-prefix", paste0("Figure3Data/MacaquePeaksInHuman/aparc/DifferenceMaps/", "M.Ranked.", measure)))
}

generateDifferenceMaps <- function(aparcPeaks, type) {
  aparcPeaks$MacaqueRanked <- rank(aparcPeaks$Macaque)
  aparcPeaks$HumanRanked <- rank(aparcPeaks$Human)
  aparcPeaks$RankDiff <- aparcPeaks$HumanRanked - aparcPeaks$MacaqueRanked
  aparcPeaks$Difference[1] <- 0
  createMacaquePeakGifti(aparcPeaks$RankDiff, type)
  createVisualization(aparcPeaks$RankDiff, type, "coolwarm", -20, 20, "human", "aparc")
  return(aparcPeaks)
}

aparcPeaks[["Volume"]] <- generateDifferenceMaps(aparcPeaks[['Volume']], "Volume")
aparcPeaks[["Area"]] <- generateDifferenceMaps(aparcPeaks[['Area']], "Area")
aparcPeaks[["Thickness"]] <- generateDifferenceMaps(aparcPeaks[['Thickness']], "Thickness")
```

```{r}
system(paste("bash", "Figure3Scripts/metric2volume_RC.sh"))
```

```{r}
lh_aparc <- "../../Atlas/aparc/fs_LR.aparc.L.32k.func.gii"
rh_aparc <- "../../Atlas/aparc/fs_LR.aparc.R.32k.func.gii"
base_metric_path <- "Figure3Data/MacaquePeaksInHuman/aparc/DifferenceMaps"
n_terms <- 200
n_studies <- 10

system(paste("python3", "Figure3Scripts/image_search.py",
             "--image-path", file.path(base_metric_path, "volumes", "M.Ranked.Volume.nii.gz"),
             "--n-studies", n_studies,
             "--n-terms", n_terms,
             "--pos-neg",
             "--bins", 4,
             "--output", file.path(base_metric_path, "neuroquery", "M.Volume.Ranked")))
system(paste("python3", "Figure3Scripts/image_search.py",
             "--image-path", file.path(base_metric_path, "volumes", "M.Ranked.Area.nii.gz"),
             "--n-studies", n_studies,
             "--n-terms", n_terms,
             "--pos-neg",
             "--bins", 4,
             "--output", file.path(base_metric_path, "neuroquery", "M.Area.Ranked")))
system(paste("python3", "Figure3Scripts/image_search.py",
             "--image-path", file.path(base_metric_path, "volumes", "M.Ranked.Thickness.nii.gz"),
             "--n-studies", n_studies,
             "--n-terms", n_terms,
             "--pos-neg",
             "--bins", 4,
             "--output", file.path(base_metric_path, "neuroquery", "M.Thickness.Ranked")))
```

```{r}
## Visualize markov parcellation
lh_data <- seq(1, 92, by=1)
rh_data <- seq(1, 92, by=1)
Visualize.Surface(lh_data, rh_data, "monkey", "markov", "Plotting/Final/Figure3Images/Markov_parcellation.png", "tab20b", 1, 92)
```
