This file is for creating plots of the GAMLSS modeling section of the supplementary

```{r}
## Make QQ plots of model fits for four global phenotypes
source("../../301.functions.r")
loadModels <- function(metrics) {
  HOLDER <- list()
  basePath <- file.path("../../RDS/ASEG.VOLUME.COMBAT")
  for (metric in metrics) {
    PRIMARY <- list()
    PRIMARY$SUBSET <- readRDS(file.path(basePath, metric, "SUBSET.rds"))
    PRIMARY$MODEL <- readRDS(file.path(basePath, metric, "MODEL.rds"))
    PRIMARY$FIT.EXTRACT <- readRDS(file.path(basePath, metric, "FIT.EXTRACT.rds"))
    PRIMARY$CURVE <- Apply.Param(
      NEWData=PRIMARY$SUBSET,
      FITParam=PRIMARY$FIT.EXTRACT$param,
      Add.Normalise=TRUE,
      Add.Derivative=FALSE
    )
    PRIMARY$CURVE$residuals <- PRIMARY$CURVE[, metric] - PRIMARY$CURVE$PRED.mean.pop
    HOLDER[[metric]] <- PRIMARY
  }
  return(HOLDER)
} 
PRIMARY <- loadModels(c("TotalGrayVol", "CorticalWhiteMatterVol", "SubCortGrayVol", "Total.Lateral.Ventricle"))
```

```{r}
## Need to make QQ plots

```

```{r}
## Function for plotting mu random effect
plotMuRanef <- function(measure, title) {
  randef.ci <- readRDS(file.path("../../RDS/ASEG.VOLUME.COMBAT", measure, "MU.RANDEF.CI.rds"))
  SUBSET <- readRDS(file.path("../../RDS/ASEG.VOLUME.COMBAT", measure, "SUBSET.rds"))
  mean_age <- SUBSET %>%
    group_by(Site) %>%
    summarise(mean_age = mean(AgeTransformed))
  randef.ci$Site <- row.names(randef.ci)
  randef.ci <- merge(randef.ci, mean_age, by="Site")
  randef.ci$Site <- factor(randef.ci$Site, levels = mean_age$Site[order(mean_age$mean_age)])
  randef.ci$range <- abs(randef.ci$mu.0.975.upper - randef.ci$mu.0.025.lower)
  View(randef.ci)
  scatter <- ggplot() +
    geom_point(data = randef.ci, aes(x = mu, y = Site, color = mean_age), size = 5, alpha = 0.5) +
    geom_errorbarh(data = randef.ci, aes(xmin = mu.0.025.lower, xmax = mu.0.975.upper, y = Site), height = 0.1) +
    ylab("Site") +
    theme_classic() +
    scale_color_gradient(low = "gray", high = "red", limits=c(0, 25)) +
    theme(
      panel.grid.major.y = element_line(color = "gray", linetype = "dashed", size = 0.3)
    ) +
    ggtitle(title) +
    ggeasy::easy_center_title()
  return(scatter)
}
GMV <- plotMuRanef("TotalGrayVol", "GMV")
WMV <- plotMuRanef("CorticalWhiteMatterVol", "WMV")
sGMV <- plotMuRanef("SubCortGrayVol", "sGMV")
VENT <- plotMuRanef("Total.Lateral.Ventricle", "Ventricular Volume")
plot <- GMV + WMV + sGMV + VENT+
  plot_layout(
    guides = "collect",
    axis_titles = "collect"
  )
ggsave(plot=plot, file.path("SupplementaryGAMLSSImages/GlobalPhenotypeMu.png"), width=8, height=10, dpi=300)
ggsave(plot=plot, file.path("SupplementaryGAMLSSImages/GlobalPhenotypeMu.pdf"), width=8, height=10, dpi=300)
plot
```
## Stats on mean age vs mu effect

```{r}
plotMuRanef <- function(measure) {
  randef.ci <- readRDS(file.path("../../RDS/ASEG.VOLUME.COMBAT", measure, "MU.RANDEF.CI.rds"))
  SUBSET <- readRDS(file.path("../../RDS/ASEG.VOLUME.COMBAT", measure, "SUBSET.rds"))
  mean_age <- SUBSET %>%
    group_by(Site) %>%
    summarise(mean_age = mean(AgeTransformed))
  randef.ci$Site <- row.names(randef.ci)
  randef.ci <- merge(randef.ci, mean_age, by="Site")
  randef.ci$Site <- factor(randef.ci$Site, levels = mean_age$Site[order(mean_age$mean_age)])
  randef.ci$range <- abs(randef.ci$mu.0.975.upper - randef.ci$mu.0.025.lower)
  model <- lm(mu ~ mean_age, data = randef.ci)
  summary(model)
}
plotMuRanef("Total.Lateral.Ventricle")
```



```{r}
## Function for scatterplot with correlation
# X: Median Age
# Y: Mu ranef

plotAgeMu <- function(measure, title) {
  library(lmerTest)
  randef.ci <- readRDS(file.path("../../RDS/ASEG.VOLUME.COMBAT", measure, "MU.RANDEF.CI.rds"))
  randef.ci$Site <- row.names(randef.ci)
  SUBSET <- readRDS(file.path("../../RDS/ASEG.VOLUME.COMBAT", measure, "SUBSET.rds"))
  median_age <- SUBSET %>%
    group_by(Site) %>%
    summarise(median_age = median(Age))
  
  plotting <- merge(median_age, randef.ci, by="Site")
  plot <- ggplot(data=plotting, aes(x=median_age, y=mu)) +
    geom_point(size=3) +
    theme_minimal() +
    theme(legend.position="none", axis.line=element_line()) +
    geom_smooth(method = "lm", se = TRUE, color = "black", fill = "black", alpha = 0.3) +
    xlab("Median Age (yrs)") +
    ylab("Mu") +
    ggtitle(title) +
    ggeasy::easy_center_title()
  
  return(plot)
}

GMV <- plotAgeMu("TotalGrayVol", "GMV")
WMV <- plotAgeMu("CorticalWhiteMatterVol", "WMV")
sGMV <- plotAgeMu("SubCortGrayVol", "sGMV")
VENT <- plotAgeMu("Total.Lateral.Ventricle", "Ventricular Volume")
plot <- GMV + WMV + sGMV + VENT +
  plot_layout(
    axis_titles = "collect"
  )
ggsave(plot=plot, "SupplementaryGAMLSSImages/MuRandefAge.png", width=6, height=4, dpi=300)
ggsave(plot=plot, "SupplementaryGAMLSSImages/MuRandefAge.pdf", width=6, height=4, dpi=300)
plot
```

ASSOCIATION BETWEEN MU AND MEDIAN AGE

```{r}
library(lmerTest) 
library(dplyr) 
library(ggplot2) 
library(purrr) 
library(broom) 
library(stats) 

# Define the function to analyze multiple measures 
analyze_measures <- function(measures) { 

  # Helper function to fit linear model and extract p-value and t-score 
  fit_model <- function(measure) { 
    randef.ci <- readRDS(file.path("../../RDS/ASEG.VOLUME.COMBAT", measure, "MU.RANDEF.CI.rds")) 
    randef.ci$Site <- row.names(randef.ci) 
    SUBSET <- readRDS(file.path("../../RDS/ASEG.VOLUME.COMBAT", measure, "SUBSET.rds")) 
    median_age <- SUBSET %>% 
      group_by(Site) %>% 
      summarise(median_age = median(Age)) 

    plotting <- merge(median_age, randef.ci, by="Site") 

    model <- lm(mu ~ median_age, data=plotting) 

    # Extract t-value and p-value
    model_summary <- tidy(model)
    result <- model_summary %>% 
      filter(term == "median_age") %>% 
      select(estimate, std.error, statistic, p.value) %>% 
      rename(
        estimate = estimate,
        std_error = std.error,
        t_value = statistic,
        p_value = p.value
      ) %>% 
      as.list() %>% 
      unlist()
    
    return(result) 
  } 

  # Analyze each measure and collect results 
  results <- map_df(measures, fit_model, .id = "measure") 

  # Perform FDR correction on p-values 
  fdr_corrected <- p.adjust(results$p_value, method = "fdr") 

  # Add FDR corrected p-values to results 
  results <- results %>% 
    mutate(fdr_corrected_p_value = fdr_corrected) 

  # Print results 
  print(results) 
  return(results) 
} 

# Example usage 
measures <- c("TotalGrayVol", "CorticalWhiteMatterVol", "SubCortGrayVol", "Total.Lateral.Ventricle")  # Replace with actual measure names 
results <- analyze_measures(measures)
```

```{r}
## Function to loop through and create GAMLSS models for all the base phenotypes
refitGAMLSS <- function(PRIMARY) {
  ## TotalGrayVol
  PRIMARY$TotalGrayVol$GAMLSSRefit <- gamlss(
    formula=formula(PRIMARY$TotalGrayVol$MODEL$mu),
    sigma.formula=formula(PRIMARY$TotalGrayVol$MODEL$sigma),
    nu.formula=formula(PRIMARY$TotalGrayVol$MODEL$nu),
    family=PRIMARY$TotalGrayVol$MODEL$family,
    data=PRIMARY$TotalGrayVol$SUBSET,
    contrasts=PRIMARY$TotalGrayVol$MODEL$contrasts,
    control=gamlss.control(n.cyc=200)
  )
  predicted_values <- predict(PRIMARY$TotalGrayVol$GAMLSSRefit, newdata = PRIMARY$TotalGrayVol$SUBSET, type = "response")
  PRIMARY$TotalGrayVol$CURVE$new_predictions <- predicted_values
  
  ## CorticalWhiteMatterVol
  PRIMARY$CorticalWhiteMatterVol$GAMLSSRefit <- gamlss(
    formula=formula(PRIMARY$CorticalWhiteMatterVol$MODEL$mu),
    sigma.formula=formula(PRIMARY$CorticalWhiteMatterVol$MODEL$sigma),
    nu.formula=formula(PRIMARY$CorticalWhiteMatterVol$MODEL$nu),
    family=PRIMARY$CorticalWhiteMatterVol$MODEL$family,
    data=PRIMARY$CorticalWhiteMatterVol$SUBSET,
    contrasts=PRIMARY$CorticalWhiteMatterVol$MODEL$contrasts,
    control=gamlss.control(n.cyc=200)
  )
  predicted_values <- predict(PRIMARY$CorticalWhiteMatterVol$GAMLSSRefit, newdata = PRIMARY$CorticalWhiteMatterVol$SUBSET, type="response")
  PRIMARY$CorticalWhiteMatterVol$CURVE$new_predictions <- predicted_values
  
  ## SubCortGrayVol
  PRIMARY$SubCortGrayVol$GAMLSSRefit <- gamlss(
    formula=formula(PRIMARY$SubCortGrayVol$MODEL$mu),
    sigma.formula=formula(PRIMARY$SubCortGrayVol$MODEL$sigma),
    nu.formula=formula(PRIMARY$SubCortGrayVol$MODEL$nu),
    family=PRIMARY$SubCortGrayVol$MODEL$family,
    data=PRIMARY$SubCortGrayVol$SUBSET,
    contrasts=PRIMARY$SubCortGrayVol$MODEL$contrasts,
    control=gamlss.control(n.cyc=200)
  )
  predicted_values <- predict(PRIMARY$SubCortGrayVol$GAMLSSRefit, newdata = PRIMARY$SubCortGrayVol$SUBSET, type="response")
  PRIMARY$SubCortGrayVol$CURVE$new_predictions <- predicted_values
  
  ## Total.Lateral.Ventricle
  PRIMARY$Total.Lateral.Ventricle$GAMLSSRefit <- gamlss(
    formula=formula(PRIMARY$Total.Lateral.Ventricle$MODEL$mu),
    sigma.formula=formula(PRIMARY$Total.Lateral.Ventricle$MODEL$sigma),
    nu.formula=formula(PRIMARY$Total.Lateral.Ventricle$MODEL$nu),
    family=PRIMARY$Total.Lateral.Ventricle$MODEL$family,
    data=PRIMARY$Total.Lateral.Ventricle$SUBSET,
    contrasts=PRIMARY$Total.Lateral.Ventricle$MODEL$contrasts,
    control=gamlss.control(n.cyc=200)
  )
  predicted_values <- predict(PRIMARY$Total.Lateral.Ventricle$GAMLSSRefit, newdata = PRIMARY$Total.Lateral.Ventricle$SUBSET, type="response")
  PRIMARY$Total.Lateral.Ventricle$CURVE$new_predictions <- predicted_values
  
  return(PRIMARY)
}
PRIMARY <- refitGAMLSS(PRIMARY)
```

```{r}
## Check whether the model fits look good
ggplot(data=PRIMARY$Total.Lateral.Ventricle$CURVE) +
  geom_point(aes(x=LogAge, y=new_predictions), color="red") +
  geom_point(aes(x=LogAge, y=PRED.mean.wre), color="blue")
```
```{r}
GMV <- plot(PRIMARY$TotalGrayVol$GAMLSSRefit)
WMV <- plot(PRIMARY$CorticalWhiteMatterVol$GAMLSSRefit)
sGMV <- plot(PRIMARY$SubCortGrayVol$GAMLSSRefit)
VENT <- plot(PRIMARY$Total.Lateral.Ventricle$GAMLSSRefit)
```
```{r}
plot(PRIMARY$SubCortGrayVol$GAMLSSRefit)
```
```{r}
GMV <- dtop(PRIMARY$TotalGrayVol$GAMLSSRefit)
WMV <- dtop(PRIMARY$CorticalWhiteMatterVol$GAMLSSRefit)
sGMV <- dtop(PRIMARY$SubCortGrayVol$GAMLSSRefit)
VENT <- dtop(PRIMARY$Total.Lateral.Ventricle$GAMLSSRefit)
```

```{r}
## Plotting standard deviation against mu random effect for each study
plotAgeMuSdDev <- function(measure, title) {
  library(lmerTest)
  randef.ci <- readRDS(file.path("../../RDS/ASEG.VOLUME.COMBAT", measure, "MU.RANDEF.CI.rds"))
  randef.ci$Site <- row.names(randef.ci)
  SUBSET <- readRDS(file.path("../../RDS/ASEG.VOLUME.COMBAT", measure, "SUBSET.rds"))
  sd_age <- SUBSET %>%
    group_by(Site) %>%
    summarise(sd_age = sd(Age))
  
  plotting <- merge(sd_age, randef.ci, by="Site")
  plot <- ggplot(data=plotting, aes(x=sd_age, y=mu)) +
    geom_point(size=3) +
    theme_minimal() +
    theme(legend.position="none", axis.line=element_line()) +
    geom_smooth(method = "lm", se = TRUE, color = "black", fill = "black", alpha = 0.3) +
    xlab("Standard Deviation of Age (yrs)") +
    ylab("Mu") +
    ggtitle(title) +
    ggeasy::easy_center_title()
  
  return(plot)
}
GMV <- plotAgeMuSdDev("TotalGrayVol", "GMV")
WMV <- plotAgeMuSdDev("CorticalWhiteMatterVol", "WMV")
sGMV <- plotAgeMuSdDev("SubCortGrayVol", "sGMV")
VENT <- plotAgeMuSdDev("Total.Lateral.Ventricle", "Ventricular Volume")
plot <- GMV + WMV + sGMV + VENT +
  plot_layout(
    axis_titles = "collect"
  )
ggsave(plot=plot, "SupplementaryGAMLSSImages/MuRandefAgeSd.png", width=6, height=4, dpi=300)
ggsave(plot=plot, "SupplementaryGAMLSSImages/MuRandefAgeSd.pdf", width=6, height=4, dpi=300)
plot
```
LINEAR TEST MU VS SD OF SAMPLE AGE

```{r}
analyze_measures <- function(measures) { 

  # Helper function to fit linear model and extract p-value and t-score 
  fit_model <- function(measure) { 
    randef.ci <- readRDS(file.path("../../RDS/ASEG.VOLUME.COMBAT", measure, "MU.RANDEF.CI.rds")) 
    randef.ci$Site <- row.names(randef.ci) 
    SUBSET <- readRDS(file.path("../../RDS/ASEG.VOLUME.COMBAT", measure, "SUBSET.rds")) 
    sd_age <- SUBSET %>% 
      group_by(Site) %>% 
      summarise(sd_age = sd(Age)) 

    plotting <- merge(sd_age, randef.ci, by="Site") 

    model <- lm(mu ~ sd_age, data=plotting) 

    # Extract t-value and p-value
    model_summary <- tidy(model)
    result <- model_summary %>% 
      filter(term == "sd_age") %>% 
      select(estimate, std.error, statistic, p.value) %>% 
      rename(
        estimate = estimate,
        std_error = std.error,
        t_value = statistic,
        p_value = p.value
      ) %>% 
      as.list() %>% 
      unlist()
    
    return(result) 
  } 

  # Analyze each measure and collect results 
  results <- map_df(measures, fit_model, .id = "measure") 

  # Perform FDR correction on p-values 
  fdr_corrected <- p.adjust(results$p_value, method = "fdr") 

  # Add FDR corrected p-values to results 
  results <- results %>% 
    mutate(fdr_corrected_p_value = fdr_corrected) 

  # Print results 
  print(results) 
  return(results) 
} 
# Example usage
measures <- c("TotalGrayVol", "CorticalWhiteMatterVol", "SubCortGrayVol", "Total.Lateral.Ventricle")  # Replace with actual measure names
results <- analyze_measures(measures)
```




```{r}
## Generate plots for sample size against the Mu Random Effect
plotAgeMuSampleSize <- function(measure, title) {
  library(lmerTest)
  randef.ci <- readRDS(file.path("../../RDS/ASEG.VOLUME.COMBAT", measure, "MU.RANDEF.CI.rds"))
  randef.ci$Site <- row.names(randef.ci)
  SUBSET <- readRDS(file.path("../../RDS/ASEG.VOLUME.COMBAT", measure, "SUBSET.rds"))
  sample_size <- SUBSET %>%
    group_by(Site) %>%
    summarise(sample_size = log(n()))
  
  plotting <- merge(sample_size, randef.ci, by="Site")
  plot <- ggplot(data=plotting, aes(x=sample_size, y=mu)) +
    geom_point(size=3) +
    theme_minimal() +
    theme(legend.position="none", axis.line=element_line()) +
    geom_smooth(method = "lm", se = TRUE, color = "black", fill = "black", alpha = 0.3) +
    xlab("log(Sample Size)") +
    ylab("Mu") +
    ggtitle(title) +
    ggeasy::easy_center_title()
  
  return(plot)
}
GMV <- plotAgeMuSampleSize("TotalGrayVol", "GMV")
WMV <- plotAgeMuSampleSize("CorticalWhiteMatterVol", "WMV")
sGMV <- plotAgeMuSampleSize("SubCortGrayVol", "sGMV")
VENT <- plotAgeMuSampleSize("Total.Lateral.Ventricle", "Ventricular Volume")
plot <- GMV + WMV + sGMV + VENT +
  plot_layout(
    axis_titles = "collect"
  )
ggsave(plot=plot, "SupplementaryGAMLSSImages/MuRandefAgeSampleSize.png", width=6, height=4, dpi=300)
ggsave(plot=plot, "SupplementaryGAMLSSImages/MuRandefAgeSampleSize.pdf", width=6, height=4, dpi=300)
plot
```

```{r}
analyze_measures <- function(measures) { 

  # Helper function to fit linear model and extract p-value and t-score 
  fit_model <- function(measure) { 
    randef.ci <- readRDS(file.path("../../RDS/ASEG.VOLUME.COMBAT", measure, "MU.RANDEF.CI.rds")) 
    randef.ci$Site <- row.names(randef.ci) 
    SUBSET <- readRDS(file.path("../../RDS/ASEG.VOLUME.COMBAT", measure, "SUBSET.rds")) 
    sample_size <- SUBSET %>% 
      group_by(Site) %>% 
      summarise(sample_size = log(n())) 

    plotting <- merge(sample_size, randef.ci, by="Site") 

    model <- lm(mu ~ sample_size, data=plotting) 

    # Extract t-value and p-value
    model_summary <- tidy(model)
    result <- model_summary %>% 
      filter(term == "sample_size") %>% 
      select(estimate, std.error, statistic, p.value) %>% 
      rename(
        estimate = estimate,
        std_error = std.error,
        t_value = statistic,
        p_value = p.value
      ) %>% 
      as.list() %>% 
      unlist()
    
    return(result) 
  } 

  # Analyze each measure and collect results 
  results <- map_df(measures, fit_model, .id = "measure") 

  # Perform FDR correction on p-values 
  fdr_corrected <- p.adjust(results$p_value, method = "fdr") 

  # Add FDR corrected p-values to results 
  results <- results %>% 
    mutate(fdr_corrected_p_value = fdr_corrected) 

  # Print results 
  print(results) 
  return(results) 
} 
# Example usage
measures <- c("TotalGrayVol", "CorticalWhiteMatterVol", "SubCortGrayVol", "Total.Lateral.Ventricle")  # Replace with actual measure names
results <- analyze_measures(measures)

# Example usage
measures <- c("TotalGrayVol", "CorticalWhiteMatterVol", "SubCortGrayVol", "Total.Lateral.Ventricle")  # Replace with actual measure names
results <- analyze_measures(measures)
```

```{r}
## Run linear test on the sample size of the primary study and the mu random effect
runMuLinearTest <- function() {
  ## Calculate median age by Site
  SUBSET <- readRDS("../../RDS/ASEG.VOLUME/TotalGrayVol/SUBSET.rds")
  sample_size <- SUBSET %>%
    group_by(Site) %>%
    summarise(sample_size = n())
  
  metrics <- c("TotalGrayVol", "CorticalWhiteMatterVol", "SubCortGrayVol", "Total.Lateral.Ventricle")
  data <- data.frame(
    Site = row.names(readRDS("../../RDS/ASEG.VOLUME/TotalGrayVol/MU.RANDEF.CI.rds"))
  )
  for (metric in metrics) {
    newData <- readRDS(file.path("../../RDS/ASEG.VOLUME", metric, "MU.RANDEF.CI.rds"))
    newData$Site <- row.names(newData)
    colnames(newData)[1] <- metric
    data <- merge(data, newData[, c("Site", metric)], by="Site")
  }
  data <- merge(sample_size, data, by="Site")
  long_data <- pivot_longer(
    data, 
    cols = c("TotalGrayVol", "CorticalWhiteMatterVol", "SubCortGrayVol", "Total.Lateral.Ventricle"), 
    names_to = "metric", 
    values_to = "mu"
    )
  return(long_data)
}

muRandomEffectSampleSize <- runMuLinearTest()
result <- lmTestRandef(muRandomEffectSampleSize, "sample_size")
```

In order to check the strength of GAMLSS modeling with random effects for study harmonization, we should compare the performance of ComBat against our current approach. We should also show the results of having no batch correction at all.

<<< INSERT HERE >>>

I want to visualize all the trajectories across all parcellations.
Lets bring in the plotting functions and loop through them.

```{r}
## Scatterplot function for creating the matrix
scatter <- function(measure, metric) {
  library(ggplot2)
  data <- readRDS(file.path("../../RDS", measure, metric, "SUBSET.rds"))
  if (is.null(data)) {
    return()
  }
  scatter <- ggplot() +
    geom_point(data=data, aes_string(x="LogAge", y=metric, color="Sex"), size=2) +
    scale_colour_manual(values = c("M" = "#247BA0", "F" = "#E3170A")) +
    scale_x_continuous(
      breaks = c(log(0.452), log(1.452), log(3.452), log(6.452), log(10.452), log(30.452)),
      labels = c("Birth", "1yr", "3yr", "6yr", "10yr", "30yr")
    ) +
    theme_minimal() +
    theme(
      axis.text.x = element_text(size=10),
      axis.text.y = element_text(size=10),
      plot.title = element_text(size=12)
    ) +
    xlab("") +
    ylab("") +
    ggtitle(metric) +
    ggeasy::easy_center_title() 
  
  return(scatter)
}

loopScatterMatrix <- function(measure) {
  if (measure %in% c("MARKOV.VOLUME.COMBAT", "MARKOV.AREA.COMBAT", "MARKOV.THICKNESS.COMBAT")) {
    markovOrder <- fromJSON("../../Data/ParcellationMappings/markov_order.json")
    plots <- list()
    for (NUM in 1:length(markovOrder)) {
      plot <- scatter(measure, names(markovOrder[NUM]))
      plots[[names(markovOrder[NUM])]] <- plot
    }
    patch <- wrap_plots(
      grobs = plots,
      ncol = 7,
      nrow = 13
    ) +
      plot_layout(
        guides = "collect",
        axis_titles = "collect"
      )
    
    return(patch)
  } else if (measure == "ASEG.VOLUME.COMBAT") {
    names <- c("Left.Thalamus.Proper", "Right.Thalamus.Proper", "Left.Caudate", "Right.Caudate",
               "Left.Putamen", "Right.Putamen", "Left.Pallidum", "Right.Pallidum",
               "Left.Amygdala", "Right.Amygdala", "Left.Hippocampus", "Right.Hippocampus",
               "Left.Cerebellum.Cortex", "Right.Cerebellum.Cortex")
    plots <- list()
    for (NUM in 1:length(names)) {
      plot <- scatter(measure, names[NUM])
      plots[[NUM]] <- plot
    }
    patch <- wrap_plots(
      grobs = plots,
      ncol = 7,
      nrow = 2
    ) +
      plot_layout(
        guides = "collect",
        axis_titles = "collect"
      )
    return(patch)
  }
}

scatter <- loopScatterMatrix("ASEG.VOLUME.COMBAT")
ggsave(plot=scatter, "SupplementaryGAMLSSImages/MatrixPlots/SubcortScatter.png", width=20, height=4)
ggsave(plot=scatter, "SupplementaryGAMLSSImages/MatrixPlots/SubcortScatter.pdf", width=20, height=4)
```

```{r}
## Centile function for matrix
centiles <- function(measure, metric) {
  library(ggplot2)
  source("../../301.functions.r")
  FIT.EXTRACT <- readRDS(file.path("../../../BrainChartsCode/PRIME-DE-Lifespan/RDS", measure, metric, "FIT.EXTRACT.rds"))
  if (is.null(FIT.EXTRACT)) {
    return()
  }
  curve <- Apply.Param(
      NEWData = rbind(
        expand.grid(list(FakeAge = seq(0.452, 35, by = 0.002), Sex = "F")),
        expand.grid(list(FakeAge = seq(0.452, 35, by = 0.002), Sex = "M"))
      ),
      FITParam = FIT.EXTRACT$param
    )
  curve$LogAge <- log(curve$FakeAge)
  centile <- ggplot() +
    geom_line(data=curve, aes_string(x="LogAge", y="PRED.mean.pop", color="Sex"), size=1.5) +
    geom_line(data=curve, aes_string(x="LogAge", y="PRED.l025.pop", color="Sex"), linetype="dotted", size=1, alpha=0.6) +
    geom_line(data=curve, aes_string(x="LogAge", y="PRED.u975.pop", color="Sex"), linetype="dotted", size=1, alpha=0.6) +
    scale_colour_manual(values = c("M" = "#247BA0", "F" = "#E3170A")) +
    scale_x_continuous(
      breaks = c(log(0.452), log(1.452), log(3.452), log(6.452), log(10.452), log(30.452)),
      labels = c("Birth", "1yr", "3yr", "6yr", "10yr", "30yr")
    ) +
    theme_minimal() +
    theme(
      axis.text.x = element_text(size=10),
      axis.text.y = element_text(size=10),
      plot.title = element_text(size=12)
    ) +
    xlab("") +
    ylab("") +
    ggtitle(metric) +
    ggeasy::easy_center_title() 
  
  return(centile)
}

loopCentileMatrix <- function(measure) {
  if (measure %in% c("MARKOV.VOLUME.COMBAT", "MARKOV.AREA.COMBAT", "MARKOV.THICKNESS.COMBAT")) {
    markovOrder <- fromJSON("../../Data/ParcellationMappings/markov_order.json")
    plots <- list()
    for (NUM in 1:length(markovOrder)) {
      plot <- centiles(measure, names(markovOrder[NUM]))
      plots[[names(markovOrder[NUM])]] <- plot
    }
    patch <- wrap_plots(
      grobs = plots,
      ncol = 7,
      nrow = 13
    ) +
      plot_layout(
        guides = "collect",
        axis_titles = "collect"
      )
    
    return(patch)
  } else if (measure == "ASEG.VOLUME.COMBAT") {
    names <- c("Left.Thalamus.Proper", "Right.Thalamus.Proper", "Left.Caudate", "Right.Caudate",
               "Left.Putamen", "Right.Putamen", "Left.Pallidum", "Right.Pallidum",
               "Left.Amygdala", "Right.Amygdala", "Left.Hippocampus", "Right.Hippocampus",
               "Left.Cerebellum.Cortex", "Right.Cerebellum.Cortex")
    plots <- list()
    for (NUM in 1:length(names)) {
      plot <- centiles(measure, names[NUM])
      plots[[NUM]] <- plot
    }
    patch <- wrap_plots(
      grobs = plots,
      ncol = 7,
      nrow = 2
    ) +
      plot_layout(
        guides = "collect",
        axis_titles = "collect"
      )
    return(patch)
  }
  
}

plot <- loopCentileMatrix("MARKOV.THICKNESS.COMBAT")
ggsave(plot=plot, "SupplementaryGAMLSSImages/MatrixPlots/ThicknessCentiles.png", width=20, height=20, dpi=300)
#ggsave(plot=plot, "SupplementaryGAMLSSImages/MatrixPlots/VolumeCentiles.svg", width=20, height=20)
```

```{r}
## Matrix plots for the site curves
site.curves <- function(measure, metric) {
  if (!file.exists(file.path("../../RDS", measure, metric, "SITE.CURVES.rds"))) {
    return()
  }
  SITE.CURVE <- readRDS(file.path("../../RDS", measure, metric, "SITE.CURVES.rds"))
  PLOTTING.DF <- cbind(cat=rep(names(SITE.CURVE), sapply(SITE.CURVE, nrow)), do.call(rbind, SITE.CURVE))

  site.curve <- ggplot(data=subset(PLOTTING.DF, Sex=="M"), aes(x=LogAge, y=PRED.m500.wre, color=Site)) +
    geom_line() +
    theme_classic() +
    xlab("") +
    ylab("") +
    theme_minimal() +
    theme(
      axis.text.x = element_text(size=10),
      axis.text.y = element_text(size=10),
      plot.title = element_text(size=9),
      legend.position = "none"
    ) +
    scale_x_continuous(
      breaks = c(log(0.452), log(1.452), log(3.452), log(6.452), log(10.452), log(30.452)),
      labels = c("Birth", "1yr", "3yr", "6yr", "10yr", "30yr")
    ) +
    ggtitle(metric) +
    ggeasy::easy_center_title()
      
    return(site.curve)
}

loopSiteCurveMatrix <- function(measure) {
  markovOrder <- fromJSON("../../data_v2.0/demographics/markov_order.json")
  plots <- list()
  for (NUM in 1:length(markovOrder)) {
    plot <- site.curves(measure, names(markovOrder[NUM]))
    plots[[names(markovOrder[NUM])]] <- plot
  }
  patch <- wrap_plots(
    grobs = plots,
    ncol = 7,
    nrow = 13
  ) +
    plot_layout(
      guides = "collect",
      axis_titles = "collect"
    )
    
  return(patch)
}

plot <- loopSiteCurveMatrix("MARKOV.AREA.COMBAT")
ggsave(plot=plot, "SupplementaryGAMLSSImages/MatrixPlots/AreaSiteCurves.png", width=20, height=20)
ggsave(plot=plot, "SupplementaryGAMLSSImages/MatrixPlots/AreaSiteCurves.pdf", width=20, height=20)
```

```{r}
## Growth rate matrix plot
growth <- function(measure, metric) {
  source("../../301.functions.r")
  FIT.EXTRACT <- readRDS(file.path("../../RDS", measure, metric, "FIT.EXTRACT.rds"))
  curve <- Apply.Param(
      NEWData = rbind(
        expand.grid(list(AgeTransformed = seq(0.452, 35, by = 0.002), Sex = "F")),
        expand.grid(list(AgeTransformed = seq(0.452, 35, by = 0.002), Sex = "M"))
      ),
      FITParam = FIT.EXTRACT$param
    )
  curve$LogAge <- log(curve$AgeTransformed)
  curve <- curve %>%
    mutate(AgeTransformed = round(AgeTransformed, 3)) %>%
    group_by(Sex) %>%
    mutate(PRED.mean.pop.normalized = (PRED.mean.pop - mean(PRED.mean.pop)) / sd(PRED.mean.pop)) %>% ## IS NORMALIZING NECESSARY? 
    mutate(PRED.mean.pop.normalized.slope = c(NA, diff(PRED.mean.pop)))
  
  female_peak_index <- which.max(curve$PRED.mean.pop.normalized.slope[curve$Sex == "F"])
  female_crossing_age <- curve$LogAge[curve$Sex == "F"][female_peak_index]
  
  plot <- ggplot() +
    geom_line(data=curve, aes(x=LogAge, y=PRED.mean.pop.normalized.slope, color=Sex)) +
    geom_vline(xintercept = female_crossing_age) +
    geom_hline(yintercept = 0) +
    scale_colour_manual(values = c("M" = "#247BA0", "F" = "#E3170A")) +
    scale_x_continuous(
      breaks = c(log(0.452), log(1.452), log(3.452), log(6.452), log(10.452), log(30.452)),
      labels = c("Birth", "1yr", "3yr", "6yr", "10yr", "30yr")
    ) +
    theme_minimal() +
    theme(
      legend.position = "none",
      axis.text.x = element_text(size=10),
      axis.text.y = element_text(size=10),
      plot.title = element_text(size=9)
    ) +
    xlab("") +
    ylab("") +
    ggtitle(metric) +
    ggeasy::easy_center_title() 
    
  
  return(plot)
}  

loopGrowthMatrix <- function(measure) {
  markovOrder <- fromJSON("../../Data/ParcellationMappings/markov_order.json")
  plots <- list()
  for (NUM in 1:length(markovOrder)) {
    plot <- growth(measure, names(markovOrder[NUM]))
    plots[[names(markovOrder[NUM])]] <- plot
  }
  patch <- wrap_plots(
    grobs = plots,
    ncol = 7,
    nrow = 13
  ) +
    plot_layout(
      guides = "collect",
      axis_titles = "collect"
    )
    
  return(patch)
}

plot <- loopGrowthMatrix("MARKOV.THICKNESS.COMBAT")
ggsave(plot=plot, "SupplementaryGAMLSSImages/MatrixPlots/ThicknessGrowth.png", width=20, height=20)
ggsave(plot=plot, "SupplementaryGAMLSSImages/MatrixPlots/ThicknessGrowth.pdf", width=20, height=20)
```

